---
title       : Linear Regression Explorer
subtitle    : An Interactive Application to Develop Your Intuition of Linear Regression
author      : Uwe Neuhaus
job         : Data Wrangler
framework   : revealjs      # {io2012, html5slides, shower, dzslides, ...}
revealjs    : {theme: default, transition: zoom}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

<section>
    <h2 style="color:cyan">Linear Regression Explorer</h2>
    <h4>An Interactive Application to Develop Your Intuition of Linear Regression</h4>
    <h5 style="font-size:0.6em; padding-top:4em">Uwe Neuhaus</h5>
    <h6 style="font-size:0.6em">Data Wrangler</h6>
</section>

---
<section>
    <h2 style="color:cyan">The Aim</h2>
    <ul>
      <li class="fragment fade-in">Develop a better intuition for linear regression.</li>
      <li class="fragment fade-in">Explore the linear relationship between various variables.</li>
      <li class="fragment fade-in">Try to find the regression line interactively by hand.</li>
      <li class="fragment fade-in">Compare your own estimates with the true regression line.</li>
      <li class="fragment fade-in">Implementation as an online application (using Shiny)</li>
    </ul>
</section>

---

## Selecting the Variables

- Different variables from the mtcars data set can be selected for the x- and y-axis.
- The x-axis can be scaled (logarithmic, squared, cubed).  
  
```{r simple-plot1, fig.height = 4, fig.width = 12, fig.align = 'center', message = F, echo = F}
require(ggplot2)
require(gridExtra)
plot1<-qplot(qsec, wt, data = mtcars, xlab="1/4 mile time", ylab="weight")
plot2<-qplot(hp, mpg, data = mtcars, xlab="horsepower", ylab="milex per gallon")
plot3<-qplot(hp, mpg, data = mtcars, log="x", xlab="log(horsepower)", ylab="miles per gallon")
grid.arrange(plot1, plot2, plot3, ncol=3)
```

---

## Try to Manually Fit the Line

- The aim is to fit a regression line manually by interactively choosing the intersect and slope.
- To evaluate the selected values, the residual standard error is calculated and displayed.
  
```{r simple-plot2, fig.height = 5, fig.width = 5, fig.align = 'center', message = F, echo = F}
require(ggplot2)
plot2<-qplot(wt, mpg, data = mtcars, xlab="weight", ylab="miles per gallon") +
  geom_abline(intercept = 30, slope = -3)
plot2
```
Residual Standard Error: 5.4402930

---

## Compare with True Regression Line

- You can compare your own estimate with the true linear regressionn line.
- The minimal residual standard error and R-sqared can be displayed if desired.
  
```{r simple-plot3, fig.height = 5, fig.width = 5, fig.align = 'center', message = F, echo = F}
require(ggplot2)
plot3<-qplot(wt, mpg, data = mtcars, xlab="weight", ylab="miles per gallon") +
  geom_abline(intercept = 30, slope = -3) +
  geom_smooth(method=lm, se=3)
plot3
```
Residual standard error: 5.4402930

Minimal residual standard error: 3.1340226

R-squared: 0.4594304
